\section{Introduction}
	% Hypothese	und deren Ergebnis, wenn Hypothese ist, dass nur Theorie erfüllt, sagen: Erwartung: Theorie aus einführung (mit reflink) erfüllt
	% Ergebnisse, auch Zahlen, mindestens wenn's halbwegs Sinn ergibt
	% Was wurde gemacht
	% manche leute wollen Passiv oder "man", manche nicht

  This lab report is about low-dimensional solid state matter, mainly Transition metal dichalcogenides (TMDCs) and their behavior for different circumstances.
  Here, three different experiments are shown and the resulting data evaluated.
  At first, monolayers of two different and unknown TMDCs are made and used to measure photoluminescence.
  The objective here is firstly to show that monolayers are created using the scotch tape technique and secondly the identification of the unknown materials from their characteristic photoluminescence spectra.
  In the second experiment an hexagonal boron nitride (hBN) sample is used in a similar measurement.
  For this measurement, the objective is to find a Single-photon emitter (SPE) on the sample by identifying it through an antibunching measurement.
  Since the SPE intensity increases with higher power of the excitation laser, this dependence will also be investigated.
  Lastly, the third experiment is about the magneto-optic effect with a WS$_2$ monolayer.
  The effect of excitons on faraday rotation is observed by comparing the verdet constants of the monolayer with the underlying substrate.

  %TMDCs show several 2d-specific behaviors and monolayers can be created relatively easily by exfoliation.

  %Single-photon emitters can be essential for certain types of quantum computers and quantum simulators.
